Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-11 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Citations fixed.

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BezmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}). There are various higher-order logics \citep{BezmuellerBrownKohlhase} and various higher-order modal logics \citep{Muskens}. The calculus proposed here can be regarded as a minimalistic calculus for a rigid higher-order modal logic K without extensionality principles. With additional axioms for stronger modal logics, such as KB and S5, this calculus is sufficient to achieve the stated aim.

@@

%\bibitem[{\itshape Negri(2005)}]{negri}
%Negri, S. 2005. {\itshape Proof analysis in modal logic}. J. Philosophical Logic, vol. 34, pp. 507--544.

>>>>

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BenzmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}). There are various higher-order logics \citep{BenzmuellerBrownKohlhase} and various higher-order modal logics \citep{Muskens}. The calculus proposed here can be regarded as a minimalistic calculus for a rigid higher-order modal logic K without extensionality principles. With additional axioms for stronger modal logics, such as KB and S5, this calculus is sufficient to achieve the stated aim.

@@

\bibitem[{\itshape Muskens(2006)}]{Muskens}
Muskens, R. 2006. {\itshape Higher Order Modal Logic}. In P. Blackburn, J.F.A.K. van Benthem, and F. Wolter, editors, Handbook of Modal Logic, Studies in Logic and Practical Reasoning, pages 621-653. Elsevier, Dordrecht, 2006.
